---
title: "A Machine Learning Approach to House Price Indexes"
author: 
 Andy Krause
 -- Zillow Group
 -- Seattle, WA
date: "`r Sys.Date()`"
output: 
  html_document:
      keep_md: yes
header-includes:
  - \usepackage{setspace}\doublespacing
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = FALSE, collapse=TRUE, messages=FALSE, eval=TRUE, warning = FALSE, comment = FALSE, message = FALSE)
  knitr::opts_knit$set(root.dir = "~/projects/hpi_research/irf")
```

```{r quiet_package_load, echo=FALSE}
  suppressMessages(suppressWarnings(library(hpiR)))
  suppressMessages(suppressWarnings(library(knitr)))
  suppressMessages(suppressWarnings(library(magrittr)))
```

```{r results_load, echo=FALSE}
  data_ <- readRDS(file.path(getwd(), 'data', 'data_.rds')) 
```

### Abstract

The previously researched approaches for generating house price indexes are almost exclusively found in the realm of traditional statistics, ranging from simple median calculation to complex multiple regression formats. This paper offers a new approach, using a maching learning model class -- random forests -- combined with a model-agnostic interpretability method -- partial dependency -- to derive home price indexes. After developing this method and providing an example, I then test the Interpretable Random Forest (IRF) approach against a repeat sales model and a hedonic pricing model approach.  Using data from the City of Seattle, my comparison suggests that the IRF is competitive (and occasionally superior to) existing methods across measures of accuracy, volatility and revision.

