---
title: "IRF Paper: Comparative Analysis"
author: "Andy Krause"
date: "August 24, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script should be run only after executing the "IRF: Index Generation" script (*irf_index_generation.rmd*) first as it uses those output as inputs. 

## Setup

```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = TRUE)
  knitr::opts_knit$set(root.dir = "~/projects/hpi_research/irf/papers")
  setwd(file.path(getwd(), 'papers'))
```

We begin by loading the necessary libraries.  All three of these are found on CRAN and should be installable via the `install.packages()` function.  

```{r }
  library(hpiR)
  library(tidyverse)
  library(ggplot2)
```

Next we load the pre-computed data, index and series objects from `/index_generation_script.rmd`. 

```{r}
  rt_df <- readRDS(file = file.path(getwd(), '../data/rt_df.RDS'))
  he_df <- readRDS(file = file.path(getwd(), '../data/he_df.RDS'))

  rt_hpi <- readRDS(file = file.path(getwd(), '../data/rt_hpi.RDS'))
  rt_series <- readRDS(file = file.path(getwd(), '../data/rt_series.RDS'))

  hed_hpi <- readRDS(file = file.path(getwd(), '../data/he_hpi.RDS'))
  hed_series <- readRDS(file = file.path(getwd(), '../data/he_series.RDS'))

  rf_hpi <- readRDS(file = file.path(getwd(), '../data/rf_hpi.RDS'))
  rf_series <- readRDS(file = file.path(getwd(), '../data/rf_series.RDS'))
  
  geo_results <- readRDS(file = file.path(getwd(), '../data/geo_results.RDS'))
```

## Example

We create an example dataset in order to visualize what the ICE and PD analyses look like.  

First we load the raw Seattle data.  We only need a small portion of it (sales from area 44 from 2013 onwards)

```{r}
  data(seattle_sales, package = 'hpiR')
  ex_df <- seattle_sales %>% 
    dplyr::filter(sale_date >= as.Date('2013-01-01') & 
                  area == 44)
```

We then convert this data into a hedonic dataset for use in the `hpiR` package. We use monthly periodicity.  

```{r}
  exhed_df <- hedCreateTrans(trans_df = ex_df,
                             prop_id = 'pinx',
                             trans_id = 'sale_id',
                             price = 'sale_price',
                             date = 'sale_date',
                             periodicity = 'monthly')
```

We specify the random forest model and estimate it, using the `ranger` package. 

```{r}
  rf_spec <- formula(log(price) ~ tot_sf + baths + beds + age + latitude + longitude + trans_period)
  
  rf_model <- ranger::ranger(rf_spec,
                             data = exhed_df,
                             num.tree = 500,
                             seed = 1)
```

Using this trained model, we then calculate the Individual Conditional Expectation for all observations in the training data. 

```{r}

  sim_df <- rfSimDf(rf_df = exhed_df,
                    seed = seed)

  iceall_df <- vector('list', nrow(sim_df))
  
  for (k in 1:nrow(sim_df)){
    iceall_df[[k]] <- 
      pdp::partial(object = rf_model,
                   train = sim_df[k, ],
                   pred.var = "trans_period",
                   pred.grid = data.frame(trans_period = 1:max(exhed_df$trans_period))) %>% 
      dplyr::mutate(obs = k)
  }

```
  
Using the same trained model, we then extract the partial dependency.   
  
```{r}
  pd_df <- pdp::partial(object = rf_model,
                        train = sim_df,
                        pred.var = "trans_period",
                        pred.grid = data.frame(trans_period = 1:max(exhed_df$trans_period)))

```

We collapse the ICEs and the PD into a single data.frame.

```{r}
  iceall_df <- iceall_df %>% 
    dplyr::bind_rows(., pd_df %>% 
                       dplyr::mutate(obs = 0))

  explot_df <- iceall_df %>%
    dplyr::mutate(price = exp(yhat)) %>%
    dplyr::rename(time = trans_period)

```

A plot showing the ICEs and the PD:

```{r}
  ggplot(explot_df,
         aes(x = time, y = price, group = obs)) + 
  geom_line(alpha = .3) + 
  geom_line(data = explot_df %>% dplyr::filter(obs == 0), 
            aes(x = time, y = price),
            color = 'red', size = 2) + 
  coord_cartesian(ylim = c(350000, 1200000))

```

## Indexes

We start by extracting the global indexes from the pre-computed objects. 

```{r}

 index_gdf <- dplyr::bind_rows(data.frame(Model = 'Repeat Sales', 
                                          index = rt_hpi$index$value, 
                                          time = 1:84),
                              data.frame(Model = 'Hedonic', 
                                         index = hed_hpi$index$value, 
                                         time = 1:84),
                              data.frame(Model = 'IRF', 
                                         index = rf_hpi$index$value, 
                                         time = 1:84)) %>%
  dplyr::mutate(Model = forcats::fct_relevel(as.factor(Model), 
                                             c('Repeat Sales', 'Hedonic', 'IRF')))
```

To prepare the global indexes to be added to the local indexes, we add an area number to it (0)

```{r}
  index_gdf <- index_gdf %>% 
    dplyr::mutate(region = 0,
                  Model = forcats::fct_relevel(as.factor(index_gdf$Model), 
                                             c('Repeat Sales', 'Hedonic', 'IRF')))
```

We then extract all of the local indexes.

```{r}
  index_ldf <- purrr::map2(.x = geo_results,
                           .y = names(geo_results),
                           .f = function(x, y){
                         
                       dplyr::bind_rows(data.frame(Model = 'Repeat Sales',
                                                   region = y,
                                                   index = x$rt_hpi$index$value,
                                                   time = 1:84),
                                        data.frame(Model = 'Hedonic',
                                                   region = y,
                                                   index = x$he_hpi$index$value,
                                                   time = 1:84),
                                        data.frame(Model = 'IRF',
                                                   region = y,
                                                   index = x$rf_hpi$index$value,
                                                   time = 1:84))}) %>%
  dplyr::bind_rows() %>%
  dplyr::mutate(Model = forcats::fct_relevel(as.factor(Model), 
                                             c('Repeat Sales', 'Hedonic', 'IRF')))
```

## Accuracy

We begin by assembling all of the accuracy data into a single data.frame, first for the global models, then for the local ones. 

To the global data we then add information on the model, accr, pred_price and individual error values. 

```{r glob_accr_data}
accr_gdf <- 
  dplyr::bind_rows(
    rt_hpi$index$kf_accuracy %>% dplyr::mutate(accr = 'kf', model = 'rt'),
    rt_series$pr_accuracy %>% dplyr::mutate(accr = 'pr', model = 'rt'),
    hed_hpi$index$kf_accuracy %>% dplyr::mutate(accr = 'kf', model = 'he'),
    hed_series$pr_accuracy %>% dplyr::mutate(accr = 'pr', model = 'he'),
    rf_hpi$index$kf_accuracy %>% dplyr::mutate(accr = 'kf', model = 'rf'),
    rf_series$pr_accuracy %>% dplyr::mutate(accr = 'pr', model = 'rf')) 

accr_gdf <-
  rt_df %>%
  dplyr::select(-prop_id) %>%
  dplyr::inner_join(., accr_gdf %>%
                      dplyr::select(pair_id, model, accr, pred_price, error, log_error),
                    by = 'pair_id')

```

Next, we create summary and print data.frame from this data

```{r glob_accr_summ}

 gaccr_sdf <- accr_gdf %>%
  dplyr::group_by(model, accr) %>%
  dplyr::summarize(MAPE = median(abs(log_error)),
                   MPE = median(log_error)) 

 gaccr_pdf <- cbind(gaccr_sdf %>% dplyr::filter(accr == 'kf'),
                       gaccr_sdf %>% dplyr::filter(accr == 'pr')) %>%
  dplyr::select(model, MAPE_KF = MAPE, MPE_KF = MPE, MAPE_PR = MAPE1, MPE_PR = MPE1) %>%
  dplyr::ungroup() %>%
  dplyr::rename(Model = model) %>%
  dplyr::mutate(MAPE_KF = round(MAPE_KF, 4), MPE_KF = round(MPE_KF, 4),
                MAPE_PR = round(MAPE_PR, 4), MPE_PR = round(MPE_PR, 4),
                Model = c('Hedonic', 'RandomForest', 'RepeatTrans'))

  knitr::kable(gaccr_pdf[c(3,1,2), ])
  
```

We then do the same for the local models.  One set of extractions for the k-fold results and one for the prediction results. 

K-fold

```{r loc_accr_data}

kfaccr_df <- purrr::map2(.x = geo_results,
                       .y = names(geo_results),
                       .f = function(x,y){
                        
                          rt <- x$rt_hpi$index$kf_accuracy %>%
                            dplyr::mutate(model = 'rt', 
                                          region = y)
                          he <- x$he_hpi$index$kf_accuracy %>%
                            dplyr::mutate(model = 'he', 
                                          region = y)
                          rf <- x$rf_hpi$index$kf_accuracy %>%
                            dplyr::mutate(model = 'rf', 
                                          region = y)
                          
                          dplyr::bind_rows(rt, he, rf)
                        }) %>%
  dplyr::bind_rows(.)
```

Prediction

```{r}
praccr_df <- purrr::map2(.x = geo_results,
                       .y = names(geo_results),
                       .f = function(x,y){
                        
                          rt <- x$rt_series$pr_accuracy %>%
                            dplyr::mutate(model = 'rt', 
                                          region = y)
                          he <- x$he_series$pr_accuracy %>%
                            dplyr::mutate(model = 'he', 
                                          region = y)
                          rf <- x$rf_series$pr_accuracy %>%
                            dplyr::mutate(model = 'rf', 
                                          region = y)
                          
                          dplyr::bind_rows(rt, he, rf)
                        }) %>%
  dplyr::bind_rows(.)
```

We then combine these into the local accuracy results

```{r}
 accr_ldf <- dplyr::bind_rows(kfaccr_df %>% dplyr::mutate(accr = 'kf'),
                              praccr_df %>% dplyr::mutate(accr = 'pr')) %>%
  dplyr::left_join(., rt_df, by = 'pair_id')

```

A summary and a printable data.frame are built.

```{r}

 laccr_sdf <- accr_ldf %>%
  dplyr::group_by(model, accr) %>%
  dplyr::summarize(MAPE = median(abs(log_error), na.rm = TRUE),
                   MPE = median(log_error, na.rm = TRUE)) 

 laccr_pdf <- cbind(laccr_sdf %>% dplyr::filter(accr == 'kf'),
                       laccr_sdf %>% dplyr::filter(accr == 'pr')) %>%
  dplyr::select(model, MAPE_KF = MAPE, MPE_KF = MPE, MAPE_PR = MAPE1, MPE_PR = MPE1) %>%
  dplyr::ungroup() %>%
  dplyr::rename(Model = model) %>%
  dplyr::mutate(MAPE_KF = round(MAPE_KF, 4), MPE_KF = round(MPE_KF, 4),
                MAPE_PR = round(MAPE_PR, 4), MPE_PR = round(MPE_PR, 4),
                Model = c('Hedonic', 'RandomForest', 'RepeatTrans'))

  knitr::kable(laccr_pdf[c(3,1,2), ])
  
```

## Volatility

We being by extracting the global volatility numbers

```{r}
vol_gdf <- data.frame(model = c('rt', 'hed', 'rf'),
                      mean_volatility = c(rt_hpi$index$volatility$mean,
                                            hed_hpi$index$volatility$mean,
                                            rf_hpi$index$volatility$mean))
  knitr::kable(vol_gdf %>% dplyr::mutate(Model = c('RepeatTrans', 'Hedonic', 'RandomForest'),
                                         Volatility = round(mean_volatility, 4)) %>%
                 dplyr::select(Model, Volatility))
  
```

To aid the plot, we create an annotation layer

```{r}
  ganno_df <- data.frame(Model = c('Repeat Sales', 'Hedonic', 'IRF'),
                        xpos = 73, ypos = 105,
                        lab = paste0('Vol: ', round(vol_gdf$mean_volatility, 3))) %>%
  dplyr::mutate(Model = forcats::fct_relevel(as.factor(Model), 
                                             c('Repeat Sales', 'Hedonic', 'IRF')))
```

Plot comparing indexes and volatilities

```{r}
  gindex_plot <- ggplot(index_gdf, aes(x = time, y = index, group = Model)) + 
    geom_line(color = 'black', size = 1) + 
    geom_text(data = ganno_df, aes(x = xpos,  y = ypos, label = lab), color = 'black') + 
    facet_wrap(~Model) + 
    scale_x_continuous(breaks = c(1,25,49,73), labels = c(2010, 2012, 2014, 2016)) +
    xlab("") + 
    ylab('Index Value\n')+
    theme(legend.position="none",
          plot.title = element_text(hjust = 0.5))

  gindex_plot
```

We then extract the local volatilities.

```{r}
vol_ldf <- purrr::map2(.x = geo_results,
                    .y = names(geo_results),
                    .f = function(x, y){
                        
                     data.frame(model = c('rt', 'he', 'rf'),
                                region = y,
                                volatility = c(x$rt_hpi$index$volatility$mean,
                                               x$he_hpi$index$volatility$mean,
                                               x$rf_hpi$index$volatility$mean))}) %>%
  dplyr::bind_rows()
```

Summarizing into a table

```{r}
lvol_sdf <- vol_ldf %>%
  dplyr::group_by(model) %>%
  dplyr::summarize(mean = mean(volatility))

```

Creating an annotation layer for the plot

```{r}
  lanno_df <- data.frame(Model = c('Hedonic', 'IRF', 'Repeat Sales'),
                         xpos = 67, ypos = 67, region = 0, 
                         lab = paste0('Vol: ', round(lvol_sdf$mean, 3))) %>%
  dplyr::mutate(Model = forcats::fct_relevel(as.factor(Model), 
                                             c('Repeat Sales', 'Hedonic', 'IRF')))
```

Plotting local indexes with volatility. 

```{r}
  lindex_plot <- ggplot(index_ldf, aes(x = time, y = index, group = region)) + 
    geom_line(alpha = .4)  + 
    coord_cartesian(ylim = c(50, 250)) + 
    geom_line(data = index_gdf, aes(x = time, y = index, group = region), 
              color = 'red', size = 1)+ 
    facet_wrap(~Model) + 
    annotate("rect", xmin = 51, xmax = 83, ymin = 58, ymax = 78, col = 'gray93',
             fill = 'gray93') +
    geom_text(data = lanno_df, aes(x = xpos,  y = ypos, label = lab), color = 'black') + 
    scale_x_continuous(breaks = c(1,25,49,73), labels = c(2010, 2012, 2014, 2016)) +
    xlab('') + ylab('Index Value\n') + 
    theme(legend.position="none",
          plot.title = element_text(hjust = 0.5)) + 
    ggtitle('Local Index Variation by Model')
   lindex_plot
   
```


### Revision

```{r}

  grev_mdf <- purrr::map2(.x = geo_results,
                         .y = names(geo_results),
                         .f = function(x, y){
                                data.frame(model = c('Repeat Sales', 'Hedonic', 'IRF'),
                                           region = y,
                                           revision = c(x$rt_series$revision$mean,
                                                        x$he_series$revision$mean,
                                                        x$rf_series$revision$mean))}) %>%
    dplyr::bind_rows()

  grev_sdf <- grev_mdf %>%
    dplyr::group_by(model) %>%
    dplyr::summarize(mean = mean(revision),
                     ameam = mean(abs(revision)))

  grev_gdf <- dplyr::bind_rows(rt_series$revision$period %>% 
                                dplyr::mutate(model = 'Repeat Sales'),
                               hed_series$revision$period %>% 
                                dplyr::mutate(model = 'Hedonic'),
                               rf_series$revision$period %>% 
                                dplyr::mutate(model = 'IRF'))

```


<!-- ```{r} -->
<!--  grev_plot <- ggplot(grev_gdf, aes(x = period, y = median, color = model, size = model)) +  -->
<!--   geom_line() + -->
<!--     scale_x_continuous(breaks = seq(1,85, 12), labels = 2010:2017) + -->
<!--     xlab("") +  -->
<!--     ylab('Mean Index Revision\n')+ -->
<!--     scale_color_manual(name = '', values = c('black', 'gray70', 'gray35'))+ -->
<!--     scale_size_manual(name = '', values = c(2,1,1)) + -->
<!--     theme(legend.position="bottom", -->
<!--           plot.title = element_text(hjust = 0.5)) +  -->
<!--   ggtitle('Mean Index Revision by Period (By Model)') -->
<!--  grev_plot -->

<!-- ``` -->

<!-- ```{r} -->

<!-- grev_gdf$index = c(index_gdf$index[2:84] - index_gdf$index[1:83],  -->
<!--                   index_gdf$index[86:168] - index_gdf$index[85:167],  -->
<!--                   index_gdf$index[170:252] - index_gdf$index[169:251]) -->
<!-- grev_gdf$model <- c(rep('RepeatTrans', 83), rep('Hedonic', 83), rep('RandomForest', 83)) -->
<!-- grev_gdf$model <- forcats::fct_relevel(as.factor(grev_gdf$model),  -->
<!--                                              c('RepeatTrans', 'Hedonic', 'RandomForest')) -->

<!-- grev_delta_plot <- ggplot(grev_gdf, aes(x = index, y = median, color = model)) +  -->
<!--   geom_point(color = 'gray50') +  -->
<!--   geom_smooth(method = "lm", fill = NA, color = 'black') + -->
<!--   facet_wrap(~model, ncol = 3) + -->
<!--   xlab("\nPeriod Change in Index") +  -->
<!--   ylab('Mean Index Revision\n') + -->
<!--   theme(legend.position="none", -->
<!--           plot.title = element_text(hjust = 0.5)) +  -->
<!--   ggtitle('Mean Index Revision by Index Change') +  -->
<!--   geom_rug(color = 'black', alpha = .4) -->
<!-- grev_delta_plot -->

<!-- ``` -->



<!-- ```{r} -->

<!-- rev_ldf <- purrr::map2(.x = geo_results, -->
<!--                        .y = names(geo_results), -->
<!--                        .f = function(x, y){ -->
<!--                          dplyr::bind_rows(data.frame(model = 'RepeatTrans', -->
<!--                                                      region = y, -->
<!--                                                      indexdif = x$rt_hpi$index$value[2:84] -  -->
<!--                                                        x$rt_hpi$index$value[1:83], -->
<!--                                                      rev = x$rt_series$revision$period$mean), -->
<!--                                           data.frame(model = 'Hedonic', -->
<!--                                                      region = y, -->
<!--                                                      indexdif = x$he_hpi$index$value[2:84] -  -->
<!--                                                        x$he_hpi$index$value[1:83], -->
<!--                                                      rev = x$he_series$revision$period$mean), -->
<!--                                           data.frame(model = 'RandomForest', -->
<!--                                                      region = y, -->
<!--                                                      indexdif = x$rf_hpi$index$value[2:84] -  -->
<!--                                                        x$rf_hpi$index$value[1:83], -->
<!--                                                      rev = x$rf_series$revision$period$mean))}) %>% -->
<!--   dplyr::bind_rows() %>% -->
<!--   dplyr::mutate(model = forcats::fct_relevel(as.factor(model),  -->
<!--                                              c('RepeatTrans', 'Hedonic', 'RandomForest'))) -->
<!-- ``` -->

<!-- ```{r} -->

<!-- lrev_delta_plot <- ggplot(rev_ldf, aes(x = indexdif, y = rev)) +  -->
<!--   geom_point(color = 'gray50', size = .5) +  -->
<!--   geom_smooth(method = "lm", fill = NA, color = 'black') +  -->
<!--   facet_wrap(~model, scales = 'free_x') + -->
<!--   coord_cartesian(ylim= c(-5, 5)) + -->
<!--   geom_hline(yintercept = 0, linetype = 3, color = 'gray20') + -->
<!--   xlab('\n Change in Index') + -->
<!--   ylab('Mean Period Revision\n')  + -->
<!--   theme(legend.position="none", -->
<!--           plot.title = element_text(hjust = 0.5)) +  -->
<!--   ggtitle('Revision vs Index Change by Period (Local Models)') +  -->
<!--   geom_rug(alpha = .05) -->
<!-- lrev_delta_plot -->

<!-- ``` -->











```{r}

  results_ <- list(explot = explot_df,
                   index_g = index_gdf,
                   index_l = index_ldf,
                   accr_g = gaccr_pdf,
                   accr_l = laccr_pdf,
                   vol_g = vol_gdf,
                   vol_l = vol_ldf)
  saveRDS(results_, '../data/results_.RDS')
  
```



### Spatial Dependence

```{r}
  
 accr_gdf$latitude <- he_df$latitude[match(accr_gdf$trans_id2, he_df$trans_id)]
 accr_gdf$longitude <- he_df$longitude[match(accr_gdf$trans_id2, he_df$trans_id)]

 accr_ldf$latitude <- he_df$latitude[match(accr_ldf$trans_id2, he_df$trans_id)]
 accr_ldf$longitude <- he_df$longitude[match(accr_ldf$trans_id2, he_df$trans_id)]
  
 hpiMI <- function(accr_df, model_type, accr_type, knn){
   
   accr_df <- accr_df %>% dplyr::filter(model == model_type & accr == accr_type) %>%
     dplyr::distinct(pair_id, .keep_all = TRUE)
   accr_sf <- sf::st_as_sf(accr_df, coords= c('longitude', 'latitude'))
   nb_obj <- spdep::knn2nb(spdep::knearneigh(accr_sf, knn))
   nbl_obj <- spdep::nb2listw(nb_obj, style="W", zero.policy=T)
   lm_obj <- lm(log_error ~ 1, data = accr_sf)
   mi <- spdep::lm.morantest(lm_obj, listw = nbl_obj)
   mi
   
 }
 
```
 
 
```{r}

 mi_5_kf <- list(grt_kf <- hpiMI(accr_gdf, 'rt', 'kf', 5),
                 ghe_kf <- hpiMI(accr_gdf, 'he', 'kf', 5),
                 grf_kf <- hpiMI(accr_gdf, 'rf', 'kf', 5),
                 lrt_kf <- hpiMI(accr_ldf, 'rt', 'kf', 5),
                 lhe_kf <- hpiMI(accr_ldf, 'he', 'kf', 5),
                 lrf_kf <- hpiMI(accr_ldf, 'rf', 'kf', 5))
 mi_10_kf <- list(grt_kf <- hpiMI(accr_gdf, 'rt', 'kf', 10),
                 ghe_kf <- hpiMI(accr_gdf, 'he', 'kf', 10),
                 grf_kf <- hpiMI(accr_gdf, 'rf', 'kf', 10),
                 lrt_kf <- hpiMI(accr_ldf, 'rt', 'kf', 10),
                 lhe_kf <- hpiMI(accr_ldf, 'he', 'kf', 10),
                 lrf_kf <- hpiMI(accr_ldf, 'rf', 'kf', 10))
 mi_25_kf <- list(grt_kf <- hpiMI(accr_gdf, 'rt', 'kf', 25),
                 ghe_kf <- hpiMI(accr_gdf, 'he', 'kf', 25),
                 grf_kf <- hpiMI(accr_gdf, 'rf', 'kf', 25),
                 lrt_kf <- hpiMI(accr_ldf, 'rt', 'kf', 25),
                 lhe_kf <- hpiMI(accr_ldf, 'he', 'kf', 25),
                 lrf_kf <- hpiMI(accr_ldf, 'rf', 'kf', 25))
 mi_5_pr <- list(grt_pr <- hpiMI(accr_gdf, 'rt', 'pr', 5),
                 ghe_pr <- hpiMI(accr_gdf, 'he', 'pr', 5),
                 grf_pr <- hpiMI(accr_gdf, 'rf', 'pr', 5),
                 lrt_pr <- hpiMI(accr_ldf, 'rt', 'pr', 5),
                 lhe_pr <- hpiMI(accr_ldf, 'he', 'pr', 5),
                 lrf_pr <- hpiMI(accr_ldf, 'rf', 'pr', 5))
 mi_10_pr <- list(grt_pr <- hpiMI(accr_gdf, 'rt', 'pr', 10),
                 ghe_pr <- hpiMI(accr_gdf, 'he', 'pr', 10),
                 grf_pr <- hpiMI(accr_gdf, 'rf', 'pr', 10),
                 lrt_pr <- hpiMI(accr_ldf, 'rt', 'pr', 10),
                 lhe_pr <- hpiMI(accr_ldf, 'he', 'pr', 10),
                 lrf_pr <- hpiMI(accr_ldf, 'rf', 'pr', 10))
 mi_25_pr <- list(grt_pr <- hpiMI(accr_gdf, 'rt', 'pr', 25),
                 ghe_pr <- hpiMI(accr_gdf, 'he', 'pr', 25),
                 grf_pr <- hpiMI(accr_gdf, 'rf', 'pr', 25),
                 lrt_pr <- hpiMI(accr_ldf, 'rt', 'pr', 25),
                 lhe_pr <- hpiMI(accr_ldf, 'he', 'pr', 25),
                 lrf_pr <- hpiMI(accr_ldf, 'rf', 'pr', 25))
 
 mi_ <- list(kf = list(mi5 = mi_5_kf,
                       mi10 = mi_10_kf,
                       mi25 = mi_25_kf),
             pr = list(mi5 = mi_5_pr,
                       mi10 = mi_10_pr,
                       mi25 = mi_25_pr))
```

```{r}

 mi_df <- data.frame(model = rep(c('rt', 'he', 'rf'), 12),
                     accr = c(rep('kf', 18), rep('pr', 18)),
                     scale = rep(c(rep('global', 3), rep('local', 3)), 6),
                     knn = rep(c(rep(5,6), rep(10,6), rep(25, 6)), 2),
                     mi = c(as.numeric(unlist(lapply(mi_$kf, 
                                  function(x) lapply(x, function(x) x$statistic)))),
                                as.numeric(unlist(lapply(mi_$kf, 
                                  function(x) lapply(x, function(x) x$statistic)))))) %>%
  dplyr::mutate(knn = as.factor(knn))

  mi_pdf <- mi_df %>%
  dplyr::mutate(model = ifelse(model == 'he', 'Hedonic', ifelse(model == 'rt', "RepeatTrans", 
                                                                'RandomForest')),
                accr = ifelse(accr == 'kf', 'K-Fold', 'Prediction')) %>%
  dplyr::mutate(model = forcats::fct_relevel(as.factor(model), 
                                             c('RepeatTrans', 'Hedonic', 'RandomForest')))

```

```{r}
  ggplot(mi_pdf, 
         aes(x = scale, y = mi, group = knn, color = knn)) + 
    geom_point() + 
    facet_grid(model~accr) + 
    geom_line() + 
    scale_color_manual(name = 'KNN Count', values = c('gray30', 'gray50', 'gray70')) + 
    xlab('\n Geographic Scale of Analysis') + 
    ylab("Moran's I Statistic\n") +
    theme(legend.position = 'bottom',
          plot.title = element_text(hjust = 0.5)) + 
    annotate("rect", xmin = 0.7, xmax = 2.3, ymin = -2, ymax = 1.96, alpha = .2) +
    annotate('text', x = 1.5, y = -.8, label = 'Zone of Randomness', size = 2) + 
    coord_cartesian(ylim = c(-3, 8)) + 
    ggtitle('Spatial Dependence of Errors by Accuracy Type and Model') ->
  spdep_plot
  
```

```{r}
data_ <- list()
data_[['accr_gdf']] <- accr_gdf
data_[['gaccr_sdf']] <- gaccr_sdf
data_[['gaccr_pdf']] <- gaccr_pdf
data_[['accr_ldf']] <- accr_ldf
data_[['laccr_sdf']] <- laccr_sdf
data_[['laccr_pdf']] <- laccr_pdf
data_[['morans_i']] <- mi_
data_[['spdep_plot']] <- spdep_plot
data_[['vol_gdf']] <- vol_gdf
data_[['index_gdf']] <- index_gdf
data_[['gindex_plot']] <- gindex_plot
data_[['vol_ldf']] <- vol_ldf
data_[['lvol_sdf']] <- vol_ldf
data_[['index_ldf']] <- index_ldf
data_[['lindex_plot']] <- lindex_plot
data_[['grev_mdf']] <- grev_mdf
data_[['grev_sdf']] <- grev_sdf
data_[['grev_gdf']] <- grev_gdf
data_[['grev_plot']] <- grev_plot
data_[['grev_delta_plot']] <- grev_delta_plot
data_[['rev_ldf']] <- rev_ldf
data_[['lrev_delta_plot']] <- lrev_delta_plot
saveRDS(data_, file = file.path(getwd(), '/data/rf_pdp/data_.RDS'))

```

```{r}

gis_df <- he_df %>%
  dplyr::left_join(rt_df %>% dplyr::select(prop_id, pair_id), 
                   by = 'prop_id') %>%
  dplyr::distinct(trans_id, .keep_all = TRUE)
write.csv(gis_df, row.names = FALSE, file = '~/downloads/gis_df.csv')

sea_sf <- sf::st_read(file.path(getwd(),"/data/gis/seattle_boundary.shp"))
seaass_sf <- sf::st_read(file.path(getwd(),"/data/gis/seattle_assessment_areas.shp"))
seaass_sf <- seaass_sf %>%
  dplyr::filter(id_3 > 0) %>%
  dplyr::select(area = id_3, geometry)

sales_sf <- sf::st_as_sf(gis_df, coords = c("longitude", "latitude"), 
                 crs = 4326, agr = "constant")


```


```{r}

ggplot(seaass_sf) + 
  geom_sf(fill='gray80', color = 'white') + 
  geom_sf(data = sea_sf, color = 'black', size = 1, fill = NA) +
  theme_void() + 
  theme(panel.grid.major = element_line(colour = "white"),
          plot.title = element_text(hjust = 0.5)) ->
base_map

base_map_x <- base_map +
  ggtitle("SFR Assessment Areas")
  

```

```{r}

base_map + 
  geom_sf(data = sales_sf, color = 'black', size = .1, alpha = .5)  +
  geom_sf(data = seaass_sf, color = 'white', fill = NA) +
    geom_sf(data = sea_sf, color = 'black', size = 1, fill = NA) +
  ggtitle("All Sales (43,074)") ->
sales_map

```

```{r}

base_map + 
  geom_sf(data = sales_sf %>% dplyr::filter(!is.na(pair_id)), 
          color = 'navy', size = .1, alpha = .5) +
    geom_sf(data = seaass_sf, color = 'white', fill = NA) +
    geom_sf(data = sea_sf, color = 'black', size = 1, fill = NA) +
  ggtitle("Repeat Sales (4,067)") ->
rtsales_map

```

```{r}
png(file.path(getwd(), 'papers','rf_pdp', 'maps.png'), width=1080, height = 450)
  all_map <- gridExtra::grid.arrange(base_map_x, sales_map, rtsales_map, ncol=3)
  all_map
dev.off()
```
