---
title: "Index Generation"
author: "Andy Krause"
date: "August 24, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script generates the index and series necessary to perform the comparisons between the three approaches.  It is the first script to be run. 

## Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

We begin by loading the necessary libraries.  All three of these are found on CRAN and should be installable via the `install.packages()` function.  

```{r }
  library(hpiR)
  library(tidyverse)
  library(mlr)
```

Next we load the seattle sales data from the `hpiR` package.

```{r}
  data(seattle_sales, package = 'hpiR')
```

### Build Data

We now create two `hpiR` ready datasets from the base data (`seattle_sales`).

1. The first is a hedonic data set, complete with relevant home characteristics and the sale date converted to a monthly integer (`trans_period`), with the first month as January 2010.  

```{r}
  hed_df <- hedCreateTrans(trans_df = seattle_sales,
                           prop_id = 'pinx',
                           trans_id = 'sale_id',
                           price = 'sale_price',
                           date = 'sale_date',
                           periodicity = 'monthly')

```

An example of the data is shown below:

```{r}
  hed_df %>%
    dplyr::slice(1) %>%
    t() %>%
    as.data.frame() %>%
    setNames(., '') %>%
    knitr::kable()

```

2) We then create a repeat sales transaction dataset from the same base data.  

```{r}
  rt_df <- rtCreateTrans(trans_df = seattle_sales,
                         prop_id = 'pinx',
                         trans_id = 'sale_id',
                         price = 'sale_price',
                         date = 'sale_date',
                         periodicity = 'monthly',
                         seq_only = TRUE,
                         min_period_dist = 12)
```

An example repeat sale from this data is shown below

```{r}
  rt_df %>%
    dplyr::slice(1) %>%
    t() %>%
    as.data.frame() %>%
    setNames(., '') %>%
    knitr::kable()
```

We create this data prior to testing any of the model approaches because it is shared by all models in one way or another. 

### Set parameters

Our final preparatory step is to set the global parameters to be used by all the model:

* `max_period`: Maximum number of months to analyze
* `train_period`: Beginning training period when estimating series.  The first index in the series is 25 months long.
* `ind_var`: The independent variables to use in the hedonic and random forest models. 
* `ntrees`: The number of trees to grow in each random forest model
* `sim_count`: The number of properties to simulate in the random forest partial dependence plots

```{r}

 max_period <- 84
 train_period <- 24
 ind_var = c('use_type', 'bldg_grade', 'lot_sf', 'tot_sf', 'beds', 
                                      'baths', 'latitude', 'longitude')
 ntrees = 500
 sim_count = 500

```

## Global Analysis

### Repeat Sales

We begin by analyzing the repeat sales modeling approach.  

First we create an index across the entire 84 month period.  We use a robust estimator and log the dependent variable (the difference in price between the two sales).

```{r}
  rt_hpi <- rtIndex(trans_df = rt_df,
                    estimator = 'robust',
                    log_dep = TRUE,
                    trim_model = FALSE,
                    max_period = max_period)
```

Next, we calculate the volatility of the index.

```{r}
  rt_hpi <- calcVolatility(index = rt_hpi,
                           window = 3,
                           in_place = TRUE)
```

We then calculate the in-sample accuracy

```{r}
rt_hpi <- calcAccuracy(hpi_obj = rt_hpi,
                         test_method = 'insample',
                         test_type = 'rt',
                         in_place = TRUE,
                         in_place_name = 'is_accuracy')
```

and the k-fold accuracy of the index. 

```{r}
rt_hpi <- calcAccuracy(hpi_obj = rt_hpi,
                         test_method = 'kfold',
                         test_type = 'rt',
                         in_place = TRUE,
                         in_place_name = 'kf_accuracy')
```

We then create a series of indexes, starting with an index from periods 1 to 25, then one from 1 to 26, etc. assuming we only had the data at period 25, etc. 

```{r}
    rt_series <- createSeries(hpi_obj = rt_hpi,
                              train_period = train_period,
                              max_period = max_period,
                              smooth = TRUE)

```

From this, we then calculate the volatilities for each index in the series

```{r}
rt_series <- calcSeriesVolatility(series_obj = rt_series,
                                    window = 3,
                                    smooth = FALSE,
                                    in_place = TRUE,
                                    in_place_name = 'volatility')

```

From the series, we next calculate the average revision for each period and then average over all periods

```{r}
rt_series <- calcRevision(series_obj = rt_series,
                            in_place = TRUE,
                            in_place_name = 'revision')

```

Finally, we calculate the prediction accuracy of the index by predicting one period ahead and validating against known repeat sales. 

```{r}
  rt_series <- calcSeriesAccuracy(series_obj = rt_series,
                                  test_method = 'forecast',
                                  test_type = 'rt',
                                  smooth = FALSE,
                                  in_place = TRUE,
                                  in_place_name = 'pr_accuracy')
```

We then save the key data from the index and series for later comparison and analysis.

```{r}
   
  saveRDS(rt_df, file = file.path(getwd(), '/data/rt_df.RDS'))
  saveRDS(rt_hpi[c('index')], file = file.path(getwd(), '/data/rt_hpi.RDS'))
  saveRDS(rt_series[c('revision', 'pr_accuracy')], file = file.path(getwd(), '/data/rt_series.RDS'))

  
```

### Hedonic

Next, we run through the same progression of analyses with the hedonic modeling approach

```{r}

  he_hpi <- hedIndex(trans_df = hed_df,
                     estimator = 'robust',
                     log_dep = TRUE,
                     dep_var = 'price',
                     ind_var = ind_var,
                     trim_model = FALSE,
                     max_period = max_period,
                     smooth = TRUE)


  he_hpi <- calcVolatility(index = he_hpi,
                           window = 3,
                           in_place = TRUE)

  he_hpi <- calcAccuracy(hpi_obj = he_hpi,
                         test_method = 'insample',
                         test_type = 'rt',
                         pred_df = rt_df,
                         in_place = TRUE,
                         in_place_name = 'is_accuracy')
  
  he_hpi <- calcAccuracy(hpi_obj = he_hpi,
                         test_method = 'kfold',
                         test_type = 'rt',
                         pred_df = rt_df,
                         in_place = TRUE,
                         in_place_name = 'kf_accuracy')
  
  he_series <- createSeries(hpi_obj = he_hpi,
                                             train_period = train_period,
                                             max_period = max_period,
                                             smooth = TRUE)

  he_series <- calcSeriesVolatility(series_obj = he_series,
                                    window = 3,
                                    smooth = FALSE,
                                    in_place = TRUE,
                                    in_place_name = 'volatility')
 
  he_series <- calcRevision(series_obj = he_series,
                            in_place = TRUE,
                            in_place_name = 'revision')
  
   he_series <- calcSeriesAccuracy(series_obj = he_series,
                                  test_method = 'forecast',
                                  test_type = 'rt',
                                  pred_df = rt_df,
                                  smooth = FALSE,
                                  in_place = TRUE,
                                  in_place_name = 'pr_accuracy')

  saveRDS(hed_df, file = file.path(getwd(), '/data/he_df.RDS'))
  saveRDS(he_hpi[c('index')], file = file.path(getwd(), '/data/he_hpi.RDS'))
  saveRDS(he_series[c('revision', 'pr_accuracy')], file = file.path(getwd(), '/data/he_series.RDS'))

```

### Random Forest

Finally, we run through the same progression of analyses with the random forest approach

```{r}

  rf_hpi <- rfIndex(trans_df = hed_df,
                     estimator = 'pdp',
                     dep_var = 'price',
                     ind_var = ind_var,
                     max_period = max_period,
                     smooth = FALSE,
                     ntrees = 500,
                     sim_ids = 1:nrow(hed_df))

  rf_hpi <- calcVolatility(index = rf_hpi,
                           window = 3,
                           in_place = TRUE)

  rf_hpi <- calcAccuracy(hpi_obj = rf_hpi,
                         test_method = 'insample',
                         test_type = 'rt',
                         pred_df = rt_df,
                         in_place = TRUE,
                         in_place_name = 'is_accuracy')
  
  rf_hpi <- calcAccuracy(hpi_obj = rf_hpi,
                         test_method = 'kfold',
                         test_type = 'rt',
                         pred_df = rt_df,
                         in_place = TRUE,
                         in_place_name = 'kf_accuracy')
  
  rf_series <- createSeries(hpi_obj = rf_hpi,
                                              train_period = train_period,
                                              max_period = max_period,
                                              ntrees = 500,
                                              sim_per = 1)

  rf_series <- calcSeriesVolatility(series_obj = rf_series,
                                   window = 3,
                                     smooth = FALSE,
                                     in_place = TRUE,
                                     in_place_name = 'volatility')
 
  rf_series <- calcRevision(series_obj = rf_series,
                             in_place = TRUE,
                             in_place_name = 'revision')
  
   rf_series <- calcSeriesAccuracy(series_obj = rf_series,
                                   test_method = 'forecast',
                                   test_type = 'rt',
                                   pred_df = rt_df,
                                   smooth = FALSE,
                                   in_place = TRUE,
                                   in_place_name = 'pr_accuracy')
   
  saveRDS(rf_hpi[c('index')], file = file.path(getwd(), '/data/rf_hpi.RDS'))
  saveRDS(rf_series[c('revision', 'pr_accuracy')], file = file.path(getwd(), '/data/rf_series.RDS'))

```

### Smaller geographic scales

Next we turn to testing the same three approaches on much smaller geographic areas -- King County Assessor Zones. 

Before we estimate all three models at the smaller geographic level, we turn the above process -- index, volatility, in-sample error, k-fold error, series, prediction error and revision calculation into a custom function that can be mapped across all the subsets of data.

```{r}

modelComparison <- function(data_obj,
                            periodicity = 'monthly',
                            train_period = 24,
                            max_period = 84,
                            ntrees = 500,
                            sim_per = 1,
                            ind_var = c('use_type', 'bldg_grade', 'lot_sf', 'tot_sf', 'beds', 
                                        'baths', 'latitude', 'longitude'),
                            ...){
  

  message('****************Building Data')

  # Hedonic Data
  hed_df <- hedCreateTrans(trans_df = data_obj,
                           prop_id = 'pinx',
                           trans_id = 'sale_id',
                           price = 'sale_price',
                           date = 'sale_date',
                           periodicity = periodicity)

  # Repeat Transaction Data
  rt_df <- rtCreateTrans(trans_df = data_obj,
                         prop_id = 'pinx',
                         trans_id = 'sale_id',
                         price = 'sale_price',
                         date = 'sale_date',
                         periodicity = periodicity,
                         min_period_dist = 12)

  sim_ids <- 1:nrow(hed_df)

  message('Building Indexes')

  ## Repeat Transaction Example
  rt_hpi <- rtIndex(trans_df = rt_df,
                    estimator = 'robust',
                    log_dep = TRUE,
                    trim_model = FALSE,
                    max_period = max_period,
                    lm_recover = TRUE)

  ## Hedonic sales Example
  he_hpi <- hedIndex(trans_df = hed_df,
                     estimator = 'robust',
                     log_dep = TRUE,
                     dep_var = 'price',
                     ind_var = ind_var,
                     trim_model = FALSE,
                     max_period = max_period)

  # Random Forest
  rf_hpi <- rfIndex(trans_df = hed_df,
                     estimator = 'pdp',
                     dep_var = 'price',
                     ind_var = ind_var,
                     max_period = max_period,
                     smooth = FALSE,
                     ntrees = ntrees,
                     sim_ids = sim_ids)

  message('Comparing Index Volatilities')
  ## Volatility

  rt_hpi <- calcVolatility(index = rt_hpi,
                           window = 3,
                           in_place = TRUE)
  he_hpi <- calcVolatility(index = he_hpi,
                           window = 3,
                           in_place = TRUE)
  rf_hpi <- calcVolatility(index = rf_hpi,
                            window = 3,
                            in_place = TRUE)


  message('Comparing In-Sample Accuracy')
  ## In sample accuracy
  rt_hpi <- calcAccuracy(hpi_obj = rt_hpi,
                         test_method = 'insample',
                         test_type = 'rt',
                         in_place = TRUE,
                         in_place_name = 'is_accuracy')
  he_hpi <- calcAccuracy(hpi_obj = he_hpi,
                         test_method = 'insample',
                         test_type = 'rt',
                         pred_df = rt_df,
                         in_place = TRUE,
                         in_place_name = 'is_accuracy')
  rf_hpi <- calcAccuracy(hpi_obj = rf_hpi,
                          test_method = 'insample',
                          test_type = 'rt',
                          pred_df = rt_df,
                          in_place = TRUE,
                          in_place_name = 'is_accuracy')


  message('Comparing Out-of-Sample (KFold) Accuracy')

  ## Out of sample K Fold accuracy
  rt_hpi <- calcAccuracy(hpi_obj = rt_hpi,
                         test_method = 'kfold',
                         test_type = 'rt',
                         in_place = TRUE,
                         in_place_name = 'kf_accuracy',
                         lm_recover = TRUE)
  he_hpi <- calcAccuracy(hpi_obj = he_hpi,
                         test_method = 'kfold',
                         test_type = 'rt',
                         pred_df = rt_df,
                         in_place = TRUE,
                         in_place_name = 'kf_accuracy')
  rf_hpi <- calcAccuracy(hpi_obj = rf_hpi,
                          test_method = 'kfold',
                          test_type = 'rt',
                          pred_df = rt_df,
                          in_place = TRUE,
                          in_place_name = 'kf_accuracy',
                          ntrees = ntrees,
                          sim_per = 1)

  message('Creating Series')

  ## Series
  suppressWarnings(
    rt_series <- createSeries(hpi_obj = rt_hpi,
                              train_period = train_period,
                              max_period = max_period,
                              smooth = FALSE,
                              lm_recover = TRUE)) 

  suppressWarnings(he_series <- createSeries(hpi_obj = he_hpi,
                                             train_period = train_period,
                                             max_period = max_period,
                                             smooth = FALSE))  
                   
  suppressWarnings(rf_series <- createSeries(hpi_obj = rf_hpi,
                                              train_period = train_period,
                                              max_period = max_period,
                                              ntrees = ntrees,
                                              sim_per = 1))

  message('Comparing Series Volatilities')

  # Series Volatility
  rt_series <- calcSeriesVolatility(series_obj = rt_series,
                                    window = 3,
                                    smooth = FALSE,
                                    in_place = TRUE,
                                    in_place_name = 'volatility')

  he_series <- calcSeriesVolatility(series_obj = he_series,
                                    window = 3,
                                    smooth = FALSE,
                                    in_place = TRUE,
                                    in_place_name = 'volatility')

  rf_series <- calcSeriesVolatility(series_obj = rf_series,
                                     window = 3,
                                     smooth = FALSE,
                                     in_place = TRUE,
                                     in_place_name = 'volatility')

  message('Calculating Revisions')

  ## Revision
  rt_series <- calcRevision(series_obj = rt_series,
                            in_place = TRUE,
                            in_place_name = 'revision')
  he_series <- calcRevision(series_obj = he_series,
                            in_place = TRUE,
                            in_place_name = 'revision')
  rf_series <- calcRevision(series_obj = rf_series,
                             in_place = TRUE,
                             in_place_name = 'revision')

  message('Comparing Out-of-Sample (Prediction) Accuracy')

  ## Prediction accuracy
  rt_series <- calcSeriesAccuracy(series_obj = rt_series,
                                  test_method = 'forecast',
                                  test_type = 'rt',
                                  smooth = FALSE,
                                  in_place = TRUE,
                                  in_place_name = 'pr_accuracy')
  he_series <- calcSeriesAccuracy(series_obj = he_series,
                                  test_method = 'forecast',
                                  test_type = 'rt',
                                  pred_df = rt_df,
                                  smooth = FALSE,
                                  in_place = TRUE,
                                  in_place_name = 'pr_accuracy')
  rf_series <- calcSeriesAccuracy(series_obj = rf_series,
                                   test_method = 'forecast',
                                   test_type = 'rt',
                                   pred_df = rt_df,
                                   smooth = FALSE,
                                   in_place = TRUE,
                                   in_place_name = 'pr_accuracy')


  
  list(rt_hpi = rt_hpi['index'],
       he_hpi = he_hpi['index'],
       rf_hpi = rf_hpi['index'],
       rt_series = rt_series[c('revision', 'pr_accuracy')],
       he_series = he_series[c('revision', 'pr_accuracy')],
       rf_series = rf_series[c('revision', 'pr_accuracy')],
       summary = NULL)
}






```

We start by dividing the data into assessment areas, first removing areas 23 as it does not have enought single family and townhome sales to effectively model.  

```{r}

  geo_df <- seattle_sales %>% dplyr::filter(!area %in% 23)
  geo_ <- split(geo_df, geo_df$area)

```

We then apply the function we built above to each geographic area's data.  This function estimates all three models (indexes and series) and save the results in a large list. 

```{r}
  geo_results <- purrr::map(geo_,
                            .f = modelComparison)
```

We then save these results for later analysis as well.

```{r}
    saveRDS(geo_results, file = file.path(getwd(), '/data/geo_results.RDS'))
```

Further analysis and comparison can be found in the `irf_comparison_script.rmd` file. 
