---
title: "IRF Paper: Comparative Analysis"
author: "Andy Krause"
date: "November 22, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script should be run only after executing the "IRF: Index Generation" script (*irf_index_generation.rmd*) first as it uses those output as inputs. 

## Setup

```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = TRUE)
  #knitr::opts_knit$set(root.dir = "~/projects/hpi_research/irf/papers")
  setwd(file.path(getwd(), 'papers'))
```

We begin by loading the necessary libraries.  All three of these are found on CRAN and should be installable via the `install.packages()` function.  

```{r }
  library(hpiR)
  library(tidyverse)
  library(ggplot2)
```

Next we load the pre-computed data, index and series objects from `/index_generation_script.rmd`. 

```{r}
  rt_df <- readRDS(file = file.path(getwd(), '../data/rt_df.RDS'))
  he_df <- readRDS(file = file.path(getwd(), '../data/he_df.RDS'))

  rt_hpi <- readRDS(file = file.path(getwd(), '../data/rt_hpi.RDS'))
  rt_series <- readRDS(file = file.path(getwd(), '../data/rt_series.RDS'))

  hed_hpi <- readRDS(file = file.path(getwd(), '../data/he_hpi.RDS'))
  hed_series <- readRDS(file = file.path(getwd(), '../data/he_series.RDS'))

  rf_hpi <- readRDS(file = file.path(getwd(), '../data/rf_hpi.RDS'))
  rf_series <- readRDS(file = file.path(getwd(), '../data/rf_series.RDS'))
  
  geo_results <- readRDS(file = file.path(getwd(), '../data/geo_results.RDS'))
```

## Example

We create an example dataset in order to visualize what the ICE and PD analyses look like.  

First we load the raw Seattle data.  We only need a small portion of it (sales from area 44 from 2013 onwards)

```{r}
  data(seattle_sales, package = 'hpiR')
  ex_df <- seattle_sales %>% 
    dplyr::filter(sale_date >= as.Date('2013-01-01') & 
                  area == 44)
```

We then convert this data into a hedonic dataset for use in the `hpiR` package. We use monthly periodicity.  

```{r}
  exhed_df <- hedCreateTrans(trans_df = ex_df,
                             prop_id = 'pinx',
                             trans_id = 'sale_id',
                             price = 'sale_price',
                             date = 'sale_date',
                             periodicity = 'monthly')
```

We specify the random forest model and estimate it, using the `ranger` package. 

```{r}
  rf_spec <- formula(log(price) ~ tot_sf + baths + beds + age + latitude + longitude + trans_period)
  
  rf_model <- ranger::ranger(rf_spec,
                             data = exhed_df,
                             num.tree = 500,
                             seed = 1)
```

Using this trained model, we then calculate the Individual Conditional Expectation for all observations in the training data. 

```{r}

  sim_df <- rfSimDf(rf_df = exhed_df,
                    seed = seed)

  iceall_df <- vector('list', nrow(sim_df))
  
  for (k in 1:nrow(sim_df)){
    iceall_df[[k]] <- 
      pdp::partial(object = rf_model,
                   train = sim_df[k, ],
                   pred.var = "trans_period",
                   pred.grid = data.frame(trans_period = 1:max(exhed_df$trans_period))) %>% 
      dplyr::mutate(obs = k)
  }

```
  
Using the same trained model, we then extract the partial dependency.   
  
```{r}
  pd_df <- pdp::partial(object = rf_model,
                        train = sim_df,
                        pred.var = "trans_period",
                        pred.grid = data.frame(trans_period = 1:max(exhed_df$trans_period)))

```

We collapse the ICEs and the PD into a single data.frame.

```{r}
  iceall_df <- iceall_df %>% 
    dplyr::bind_rows(., pd_df %>% 
                       dplyr::mutate(obs = 0))

  explot_df <- iceall_df %>%
    dplyr::mutate(price = exp(yhat)) %>%
    dplyr::rename(time = trans_period)

```

A plot showing the ICEs and the PD:

```{r}
  ggplot(explot_df,
         aes(x = time, y = price, group = obs)) + 
  geom_line(alpha = .3) + 
  geom_line(data = explot_df %>% dplyr::filter(obs == 0), 
            aes(x = time, y = price),
            color = 'red', size = 2) + 
  coord_cartesian(ylim = c(350000, 1200000))

```

## Indexes

We start by extracting the global indexes from the pre-computed objects. 

```{r}

 index_gdf <- dplyr::bind_rows(data.frame(Model = 'Repeat Sales', 
                                          index = rt_hpi$index$value, 
                                          time = 1:84),
                              data.frame(Model = 'Hedonic Price', 
                                         index = hed_hpi$index$value, 
                                         time = 1:84),
                              data.frame(Model = 'Interpretable Random Forest', 
                                         index = rf_hpi$index$value, 
                                         time = 1:84)) %>%
  dplyr::mutate(model = forcats::fct_relevel(as.factor(Model), 
                                             c('Repeat Sales', 'Hedonic Price', 
                                               'Interpretable Random Forest')))
```

To prepare the global indexes to be added to the local indexes, we add an area number to it (0)

```{r}
  index_gdf <- index_gdf %>% 
    dplyr::mutate(region = 0,
                  Model = forcats::fct_relevel(as.factor(index_gdf$Model), 
                                             c('Repeat Sales', 'Hedonic Price', 'Interpretable Random Forest')))
```

We then extract all of the local indexes.

```{r}
  index_ldf <- purrr::map2(.x = geo_results,
                           .y = names(geo_results),
                           .f = function(x, y){
                         
                       dplyr::bind_rows(data.frame(Model = 'Repeat Sales',
                                                   region = y,
                                                   index = x$rt_hpi$index$value,
                                                   time = 1:84),
                                        data.frame(Model = 'Hedonic Price',
                                                   region = y,
                                                   index = x$he_hpi$index$value,
                                                   time = 1:84),
                                        data.frame(Model = 'Interpretable Random Forest',
                                                   region = y,
                                                   index = x$rf_hpi$index$value,
                                                   time = 1:84))}) %>%
  dplyr::bind_rows() %>%
  dplyr::mutate(Model = forcats::fct_relevel(as.factor(Model), 
                                             c('Repeat Sales', 'Hedonic Price', 'Interpretable Random Forest')))
```

## Accuracy

We begin by assembling all of the accuracy data into a single data.frame, first for the global models, then for the local ones. 

To the global data we then add information on the model, accr, pred_price and individual error values. 

```{r glob_accr_data}
accr_gdf <- 
  dplyr::bind_rows(
    rt_hpi$index$kf_accuracy %>% dplyr::mutate(accr = 'kf', model = 'rt'),
    rt_series$pr_accuracy %>% dplyr::mutate(accr = 'pr', model = 'rt'),
    hed_hpi$index$kf_accuracy %>% dplyr::mutate(accr = 'kf', model = 'he'),
    hed_series$pr_accuracy %>% dplyr::mutate(accr = 'pr', model = 'he'),
    rf_hpi$index$kf_accuracy %>% dplyr::mutate(accr = 'kf', model = 'rf'),
    rf_series$pr_accuracy %>% dplyr::mutate(accr = 'pr', model = 'rf')) 

accr_gdf <-
  rt_df %>%
  dplyr::select(-prop_id) %>%
  dplyr::inner_join(., accr_gdf %>%
                      dplyr::select(pair_id, model, accr, pred_price, error, log_error),
                    by = 'pair_id')

```

Next, we create summary and print data.frame from this data

```{r glob_accr_summ}

 gaccr_sdf <- accr_gdf %>%
  dplyr::group_by(model, accr) %>%
  dplyr::summarize(MAPE = median(abs(log_error)),
                   MPE = median(log_error)) 

 gaccr_pdf <- cbind(gaccr_sdf %>% dplyr::filter(accr == 'kf'),
                       gaccr_sdf %>% dplyr::filter(accr == 'pr')) %>%
  dplyr::select(model, MAPE_KF = MAPE, MPE_KF = MPE, MAPE_PR = MAPE1, MPE_PR = MPE1) %>%
  dplyr::ungroup() %>%
  dplyr::rename(Model = model) %>%
  dplyr::mutate(MAPE_KF = round(MAPE_KF, 4), MPE_KF = round(MPE_KF, 4),
                MAPE_PR = round(MAPE_PR, 4), MPE_PR = round(MPE_PR, 4),
                Model = c('Hedonic Price', 'Interpretable Random Forest', 'Repeat Sales'))

  knitr::kable(gaccr_pdf[c(3,1,2), ])
  
```

We then do the same for the local models.  One set of extractions for the k-fold results and one for the prediction results. 

K-fold

```{r loc_accr_data}

kfaccr_df <- purrr::map2(.x = geo_results,
                       .y = names(geo_results),
                       .f = function(x,y){
                        
                          rt <- x$rt_hpi$index$kf_accuracy %>%
                            dplyr::mutate(model = 'rt', 
                                          region = y)
                          he <- x$he_hpi$index$kf_accuracy %>%
                            dplyr::mutate(model = 'he', 
                                          region = y)
                          rf <- x$rf_hpi$index$kf_accuracy %>%
                            dplyr::mutate(model = 'rf', 
                                          region = y)
                          
                          dplyr::bind_rows(rt, he, rf)
                        }) %>%
  dplyr::bind_rows(.)
```

Prediction

```{r}
praccr_df <- purrr::map2(.x = geo_results,
                       .y = names(geo_results),
                       .f = function(x,y){
                        
                          rt <- x$rt_series$pr_accuracy %>%
                            dplyr::mutate(model = 'rt', 
                                          region = y)
                          he <- x$he_series$pr_accuracy %>%
                            dplyr::mutate(model = 'he', 
                                          region = y)
                          rf <- x$rf_series$pr_accuracy %>%
                            dplyr::mutate(model = 'rf', 
                                          region = y)
                          
                          dplyr::bind_rows(rt, he, rf)
                        }) %>%
  dplyr::bind_rows(.)
```

We then combine these into the local accuracy results

```{r}
 accr_ldf <- dplyr::bind_rows(kfaccr_df %>% dplyr::mutate(accr = 'kf'),
                              praccr_df %>% dplyr::mutate(accr = 'pr')) %>%
  dplyr::left_join(., rt_df, by = 'pair_id')

```

A summary and a printable data.frame are built.

```{r}

 laccr_sdf <- accr_ldf %>%
  dplyr::group_by(model, accr) %>%
  dplyr::summarize(MAPE = median(abs(log_error), na.rm = TRUE),
                   MPE = median(log_error, na.rm = TRUE)) 

 laccr_pdf <- cbind(laccr_sdf %>% dplyr::filter(accr == 'kf'),
                       laccr_sdf %>% dplyr::filter(accr == 'pr')) %>%
  dplyr::select(model, MAPE_KF = MAPE, MPE_KF = MPE, MAPE_PR = MAPE1, MPE_PR = MPE1) %>%
  dplyr::ungroup() %>%
  dplyr::rename(Model = model) %>%
  dplyr::mutate(MAPE_KF = round(MAPE_KF, 4), MPE_KF = round(MPE_KF, 4),
                MAPE_PR = round(MAPE_PR, 4), MPE_PR = round(MPE_PR, 4),
                Model = c('Hedonic Price', 'Interpretable Random Forest', 'Repeat Sales'))

  knitr::kable(laccr_pdf[c(3,1,2), ])
  
```

## Volatility

We being by extracting the global volatility numbers

```{r}
vol_gdf <- data.frame(model = c('rt', 'hed', 'rf'),
                      mean_volatility = c(rt_hpi$index$volatility$mean,
                                            hed_hpi$index$volatility$mean,
                                            rf_hpi$index$volatility$mean))
  knitr::kable(vol_gdf %>% dplyr::mutate(Model = c('Repeat Sales', 'Hedonic Price', 
                                                   'Interpretable Random Forest'),
                                         Volatility = round(mean_volatility, 4)) %>%
                 dplyr::select(Model, Volatility))
  
```

To aid the plot, we create an annotation layer

```{r}
  ganno_df <- data.frame(Model = c('Repeat Sales', 'Hedonic Price', 'Interpretable Random Forest'),
                        xpos = 73, ypos = 105,
                        lab = paste0('Vol: ', round(vol_gdf$mean_volatility, 3))) %>%
  dplyr::mutate(Model = forcats::fct_relevel(as.factor(Model), 
                                             c('Repeat Sales', 'Hedonic Price', 'Interpretable Random Forest')))
```

Plot comparing indexes and volatilities

```{r}
  gindex_plot <- ggplot(index_gdf, aes(x = time, y = index, group = Model)) + 
    geom_line(color = 'black', size = 1) + 
    geom_text(data = ganno_df, aes(x = xpos,  y = ypos, label = lab), color = 'black') + 
    facet_wrap(~Model) + 
    scale_x_continuous(breaks = c(1,25,49,73), labels = c(2010, 2012, 2014, 2016)) +
    xlab("") + 
    ylab('Index Value\n')+
    theme(legend.position="none",
          plot.title = element_text(hjust = 0.5))

  gindex_plot
```

We then extract the local volatilities.

```{r}
vol_ldf <- purrr::map2(.x = geo_results,
                    .y = names(geo_results),
                    .f = function(x, y){
                        
                     data.frame(model = c('rt', 'he', 'rf'),
                                region = y,
                                volatility = c(x$rt_hpi$index$volatility$mean,
                                               x$he_hpi$index$volatility$mean,
                                               x$rf_hpi$index$volatility$mean))}) %>%
  dplyr::bind_rows()
```

Summarizing into a table

```{r}
lvol_sdf <- vol_ldf %>%
  dplyr::group_by(model) %>%
  dplyr::summarize(mean = mean(volatility))

```

Creating an annotation layer for the plot

```{r}
  lanno_df <- data.frame(Model = c('Hedonic Price', 'Interpretable Random Forest', 'Repeat Sales'),
                         xpos = 67, ypos = 67, region = 0, 
                         lab = paste0('Vol: ', round(lvol_sdf$mean, 3))) %>%
  dplyr::mutate(Model = forcats::fct_relevel(as.factor(Model), 
                                             c('Repeat Sales', 'Hedonic Price', 'Interpretable Random Forest')))
```

Plotting local indexes with volatility. 

```{r}
  lindex_plot <- ggplot(index_ldf, aes(x = time, y = index, group = region)) + 
    geom_line(alpha = .4)  + 
    coord_cartesian(ylim = c(50, 250)) + 
    geom_line(data = index_gdf, aes(x = time, y = index, group = region), 
              color = 'red', size = 1)+ 
    facet_wrap(~Model) + 
    annotate("rect", xmin = 51, xmax = 83, ymin = 58, ymax = 78, col = 'gray93',
             fill = 'gray93') +
    geom_text(data = lanno_df, aes(x = xpos,  y = ypos, label = lab), color = 'black') + 
    scale_x_continuous(breaks = c(1,25,49,73), labels = c(2010, 2012, 2014, 2016)) +
    xlab('') + ylab('Index Value\n') + 
    theme(legend.position="none",
          plot.title = element_text(hjust = 0.5)) + 
    ggtitle('Local Index Variation by Model')
   lindex_plot
   
```

### Revision

Get the global revision numbers, by period. 

```{r}

  grev_gdf <- dplyr::bind_rows(rt_series$revision$period %>% 
                                dplyr::mutate(model = 'Repeat Sales'),
                               hed_series$revision$period %>% 
                                dplyr::mutate(model = 'Hedonic Price'),
                               rf_series$revision$period %>% 
                                dplyr::mutate(model = 'Interpretable Random Forest'))
```

Local, mean revision numbers

```{r}
  grev_mdf <- purrr::map2(.x = geo_results,
                         .y = names(geo_results),
                         .f = function(x, y){
                                data.frame(model = c('Repeat Sales', 'Hedonic Price', 
                                                     'Interpretable Random Forest'),
                                           region = y,
                                           revision = c(x$rt_series$revision$mean,
                                                        x$he_series$revision$mean,
                                                        x$rf_series$revision$mean))}) %>%
    dplyr::bind_rows()

  grev_sdf <- grev_mdf %>%
    dplyr::group_by(model) %>%
    dplyr::summarize(mean = mean(revision),
                     amean = mean(abs(revision)))
```

Plot revision by period, for global

```{r}
 grev_plot <- ggplot(grev_gdf, aes(x = period, y = median, color = model, size = model)) +
  geom_line() +
    scale_x_continuous(breaks = seq(1,85, 12), labels = 2010:2017) +
    xlab("") +
    ylab('Mean Index Revision\n')+
    scale_color_manual(name = '', values = c('black', 'gray70', 'gray35'))+
    scale_size_manual(name = '', values = c(2,1,1)) +
    theme(legend.position="bottom",
          plot.title = element_text(hjust = 0.5)) +
  ggtitle('Mean Index Revision by Period (By Model)')
 grev_plot

```

Add index numbers to revision numbers

```{r}
grev_gdf$index = c(index_gdf$index[2:84] - index_gdf$index[1:83],
                  index_gdf$index[86:168] - index_gdf$index[85:167],
                  index_gdf$index[170:252] - index_gdf$index[169:251])
grev_gdf$model <- c(rep('Repeat Sales', 83), rep('Hedonic Price', 83), rep('Interpretable Random Forest', 83))
grev_gdf$model <- forcats::fct_relevel(as.factor(grev_gdf$model),
                                             c('Repeat Sales', 'Hedonic Price', 'Interpretable Random Forest'))

```

Plot revision against price movements

```{r}
grev_delta_plot <- ggplot(grev_gdf, aes(x = index, y = median, color = model)) +
  geom_point(color = 'gray50') +
  geom_smooth(method = "lm", fill = NA, color = 'black') +
  facet_wrap(~model, ncol = 3) +
  xlab("\nPeriod Change in Index") +
  ylab('Mean Index Revision\n') +
  theme(legend.position="none",
          plot.title = element_text(hjust = 0.5)) +
  ggtitle('Mean Index Revision by Index Change') +
  geom_rug(color = 'black', alpha = .4)
grev_delta_plot
```

#### Local

Next, we extract local revision and index numbers

```{r}

rev_ldf <- purrr::map2(.x = geo_results,
                       .y = names(geo_results),
                       .f = function(x, y){
                         dplyr::bind_rows(data.frame(model = 'Repeat Sales',
                                                     region = y,
                                                     indexdif = x$rt_hpi$index$value[2:84] -
                                                       x$rt_hpi$index$value[1:83],
                                                     rev = x$rt_series$revision$period$mean),
                                          data.frame(model = 'Hedonic Price',
                                                     region = y,
                                                     indexdif = x$he_hpi$index$value[2:84] -
                                                       x$he_hpi$index$value[1:83],
                                                     rev = x$he_series$revision$period$mean),
                                          data.frame(model = 'Interpretable Random Forest',
                                                     region = y,
                                                     indexdif = x$rf_hpi$index$value[2:84] -
                                                       x$rf_hpi$index$value[1:83],
                                                     rev = x$rf_series$revision$period$mean))}) %>%
  dplyr::bind_rows() %>%
  dplyr::mutate(model = forcats::fct_relevel(as.factor(model),
                                             c('Repeat Sales', 'Hedonic Price', 'Interpretable Random Forest')))
```

Plot revision numbers against index growth

```{r}

lrev_delta_plot <- ggplot(rev_ldf, aes(x = indexdif, y = rev)) +
  geom_point(color = 'gray50', size = .5) +
  geom_smooth(method = "lm", fill = NA, color = 'black') +
  facet_wrap(~model, scales = 'free_x') +
  coord_cartesian(ylim= c(-5, 5)) +
  geom_hline(yintercept = 0, linetype = 3, color = 'gray20') +
  xlab('\n Change in Index') +
  ylab('Mean Period Revision\n')  +
  theme(legend.position="none",
          plot.title = element_text(hjust = 0.5)) +
  ggtitle('Revision vs Index Change by Period (Local Models)') +
  geom_rug(alpha = .05)
lrev_delta_plot

```

### Save Data

```{r}

  results_ <- list(explot = explot_df,
                   index_g = index_gdf,
                   index_l = index_ldf,
                   accr_g = gaccr_pdf,
                   accr_l = laccr_pdf,
                   vol_g = vol_gdf,
                   vol_l = vol_ldf,
                   rev_g = grev_gdf,
                   mrev_l = grev_mdf,
                   rev_l = rev_ldf)
  saveRDS(results_, '../data/results_.RDS')
  
```
